
# Google API

<script async defer src="https://apis.google.com/js/api.js" onload="gapiLoaded()"></script>
    <script async defer src="https://accounts.google.com/gsi/client" onload="gisLoaded()"></script>

```{r googleAPI_dep}
googleAPI_dep = function(){
  htmltools::htmlDependency(
  name="google-api",
  version="1.0.0",
  src = c(href="https://apis.google.com/js/"),
  script=list(
    src="api.js",
    async=NA,
    defer=NA),
    #onload="gapiLoaded()"),
  head='<script async defer src="https://accounts.google.com/gsi/client"></script>'
    #'<script async defer src="https://accounts.google.com/gsi/client" onload="gisLoaded()"></script>'
  )

}

```

```{js}
 function execute() {
    return gapi.client.sheets.spreadsheets.values.get({
      "spreadsheetId": "1AE7_zIHORciJF3QmFaQrWeq4c9gmhzyycOYO1FblRbk",
      "range": "Sheet1!A:E"
    })
        .then(function(response) {
                // Handle the results here (response.result has the parsed body).
                console.log("Response", response);
              },
              function(err) { console.error("Execute error", err); });
  }
  
  gapi.load("client:auth2", function() {
    gapi.auth2.init({client_id: "543220568418-nor5r7hkrmqvousgnd9pduslqi788qsb.apps.googleusercontent.com"});
  });
```


```{js}
// Authorization scopes required by the API; multiple scopes can be
// included, separated by spaces.
const SCOPES = 'https://www.googleapis.com/auth/spreadsheets.readonly';

/**
 * Callback after api.js is loaded.
 */
function gapiLoaded() {
  gapi.load('client', intializeGapiClient);
}

/**
 * Callback after the API client is loaded. Loads the
 * discovery doc to initialize the API.
 */
const DISCOVERY_DOC = 'https://sheets.googleapis.com/$discovery/rest?version=v4';

async function intializeGapiClient() {
  await gapi.client.init({
    apiKey: API_KEY,
    discoveryDocs: [DISCOVERY_DOC],
  });
  gapiInited = true;
  maybeEnableButtons();
}
function gisLoaded() {
        tokenClient = google.accounts.oauth2.initTokenClient({
          client_id: CLIENT_ID,
          scope: SCOPES,
          callback: '', // defined later
        });
        gisInited = true;
        maybeEnableButtons();
      }

```

```{js ajax}
$.get( "https://sheets.googleapis.com/v4/spreadsheets/1AE7_zIHORciJF3QmFaQrWeq4c9gmhzyycOYO1FblRbk/values/Sheet1!A%3AE?key=AIzaSyCS5NWgJamT12ABAhNpXjYEnD7Zy3sg9n0", function( data ) {
  console.log( data );
});
```

You have created a new client application that uses libraries for user authentication or authorization that will soon be deprecated. New clients must use the new libraries instead; existing clients must also migrate before these libraries are deprecated. See the [Migration Guide](https://developers.google.com/identity/gsi/web/guides/gis-migration) for more information.

GET https://sheets.googleapis.com/v4/spreadsheets/1AE7_zIHORciJF3QmFaQrWeq4c9gmhzyycOYO1FblRbk/values/Sheet1!A%3AE?key=[YOUR_API_KEY] HTTP/1.1

Authorization: Bearer [YOUR_ACCESS_TOKEN]
Accept: application/json

```{js loadClient}
function loadClient() {
    gapi.client.setApiKey("AIzaSyCS5NWgJamT12ABAhNpXjYEnD7Zy3sg9n0");
    return gapi.client.load("https://sheets.googleapis.com/$discovery/rest?version=v4")
        .then(function() { console.log("GAPI client loaded for API"); },
              function(err) { console.error("Error loading GAPI client for API", err); });
  }
```

```{js execute}
function execute() {
    return gapi.client.sheets.spreadsheets.values.get({
      "spreadsheetId": "1AE7_zIHORciJF3QmFaQrWeq4c9gmhzyycOYO1FblRbk",
      "range": "Sheet1!A:E"
    })
        .then(function(response) {
                // Handle the results here (response.result has the parsed body).
                gsResponse=response;
                console.log("Response", response);
              },
              function(err) { console.error("Execute error", err); });
  }
get_values = function(){
  gsResponse.result.values
}
```


           https://docs.google.com/spreadsheets/d/1AE7_zIHORciJF3QmFaQrWeq4c9gmhzyycOYO1FblRbk/edit?usp=sharing
```{r}
econWeb::Dependency() -> dep
htmltools::tagList(
  dep$jquery$onCloud(),
googleAPI_dep()) |> gapp$update()

```

```{r}
Sys.getenv("googleClientId") |> clipr::write_clip()
```

```{r}
dep$jquery$onCloud() |>
  gapp$update()
```

